Approximation as Differentiation

### 2025-05-24 main/formal-structures.tex
ACM requires title case for subsection headings.
Move comment about Agda impl to contribs.

\note{Probably a better way: (1) introduce the category of lattices and Galois connections, which is what we will use to interpret forward and backward approximation, and establish some properties of this category; (2) say that we want sets with each point having an associated lattice of approximations, and morphisms to match; (3) note that this is exactly the Grothendieck construction for a particular indexed category; (4) Say that CHAD is what we need here; (5) Recapitulate the bits of CHAD that we need, with our Agda formalisation; (6) Explain how we cope with higher-order structure, by using presheaves and the Yoneda embedding.}

We take an approach based on the CHAD (Combinatory Homomorphic Automatic Differentiation) of Mattias Vákár and others~\cite{vákár22,nunes2023}. Here follows a rough overview of this approach and how we have applied it to \GPS.

We have \href{https://github.com/bobatkey/approx-diff}{formalised this work in Agda}. Not only does this mean that the constructions and proofs have been checked, the construction is executable and can be run on small examples. We are also planning to use Agda's JavaScript backend to produce a demo.\todo{Do this?}

@@

\subsection{Category of lattices and Galois connections}

>>>>

Our approach to a denotational account of \GPS is based on the CHAD (Combinatory Homomorphic Automatic Differentiation) work of Mattias Vákár and others~\cite{vákár22,nunes2023}. Before we go into details, we present a high-level overview of this approach and how we have applied it to \GPS.

@@

\subsection{Category of Lattices and Galois Connections}

### 2025-05-24 main/introduction.tex
Move comment about Agda impl to contribs.

  In a simple query like this, it is easy to work out the dependency relationship between the input and output. However, the benefit of \GPS is that it is {\em automatic} for all programs, no matter how complex the relationship between input and output. Moreover, by changing what we mean by ``approximation'' we can compute a range of different information about a program.
\end{example}

@@

>>>>

  In a simple query like this, it is easy to work out the dependency relationship between the input and output. However, the benefit of \GPS, and other language-based approaches, is that it is {\em automatic} for all programs, no matter how complex the relationship between input and output. Moreover, by changing what we mean by ``approximation'' we can compute a range of different information about a program.
\end{example}

@@

We have \href{https://github.com/bobatkey/approx-diff}{formalised this work in Agda}. Not only does this mean that the constructions and proofs have been checked, but also the construction is executable and can be run on small examples. We are also planning to use Agda's JavaScript backend to produce a demo. \todo{Do this?}
